CF Registry Analysis

### 2022-12-24 Christine Chan/CF Registry/cf_registry_analysis.qmd
Update cf_registry_analysis.qmd

       `Total New Cases Age > 30` = new_cases_30,
       `Total At Risk Age > 30` = at_risk_30,
       `Total Incidence Age > 30` = inc_30)
}
incidence = lapply(2003:2018, function(y){year_inc(year = y)})
incidence = do.call(rbind,incidence)
kable(incidence,digits = 3)
```

@@

```{r}
#| label: tbl-prevalence
#| tbl-cap: "Yearly Prevalence of CFRD"
encounter %>% 
```

@@

# Questions

1.  For these calculations, do we need to just use those with an OGTT? Or everybody in the database?

>>>>

       `Total New Cases Age > 30` = new_cases_30,
       `Total At Risk Age > 30` = at_risk_30,
       `Total Incidence Age > 30` = inc_30)
}
incidence = lapply(2003:2018, function(y){year_inc(year = y)})
incidence = data.frame(do.call(rbind,incidence),check.names = F)
incidence = data.frame(lapply(incidence,as.numeric),check.names = F)
kable(incidence,digits = 3)
```

@@

```{r}
#| label: tbl-prevalence
#| tbl-cap: "Yearly Prevalence of CFRD"
encounter$cfrd_ogtt = factor(encounter$cfrd_ogtt,levels = c("No","Yes"),ordered = T)
encounter %>% group_by(eDWID,reviewyear) %>% 
  summarise(highest_2_hour_bg = suppressWarnings(max(twohour_bloodglucose,na.rm = T)),
            cfrd = max(cfrd_ogtt),
            cfrd_status = suppressWarnings(max(cfrd_status,na.rm = T)),
            .groups = "drop") %>%
  group_by(reviewyear) %>%
  summarise(`Prevalence by OGTT` = mean(as.numeric(cfrd)-1)*100,
            `Prevalence by CFFPR` = mean(cfrd_status == 3,na.rm = T)*100) %>%
  kable(.,digits = 3)
```

@@
